---
title: "ETL"
author: "Karl Nagy"
date: '2022-03-25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,error = FALSE, echo = FALSE) 
```

# Key Question:
* How have Ukraine's musical tastes changed since the invasion?
* How have Russia's musical tastes changed?
* How have Europe's musical tastes changed?

# Data
Take the top 50 in a country each day and plot it over time from 1 month before the invasion to present day (maybe repeat this for invasion of Crimea?). This should make ~3000 rows per country.

* Region/country
* genre
* danceability
* energy
* track_id
* loudness
* speechiness
* tempo
* uri
* valence
* date - 
* row_id

# Cleaning

## Packages
```{r, include=FALSE}
install.packages("tidyverse", repos='http://cran.us.r-project.org')
install.packages("here", repos='http://cran.us.r-project.org')
install.packages("spotifyr", repos='http://cran.us.r-project.org')
```

```{r}
library(tidyverse)
library(lubridate)
library(here)
library(spotifyr)
```

