---
title: "ETL"
author: "Karl Nagy"
date: '2022-03-25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,error = FALSE, echo = FALSE) 
```

# Key Question:
* How have Ukraine's musical tastes changed since the invasion?
* How have Russia's musical tastes changed?
* How have Europe's musical tastes changed?

# Data
Take the top 50 in a country each day and plot it over time from 1 month before the invasion to present day (maybe repeat this for invasion of Crimea?). This should make ~3000 rows per country.

* Region/country
* genre
* danceability
* energy
* track_id
* loudness
* speechiness
* tempo
* uri
* valence
* date - 
* row_id

# Cleaning

## Packages
```{r, include=FALSE}
install.packages("tidyverse", repos='http://cran.us.r-project.org')
install.packages("here", repos='http://cran.us.r-project.org')
install.packages("spotifyr", repos='http://cran.us.r-project.org')
install.packages("knitr", repos='http://cran.us.r-project.org')
install.packages("lubridate", repos='http://cran.us.r-project.org')

```

```{r}
library(tidyverse)
library(lubridate)
library(knitr)
library(here)
library(spotifyr)
```

```{r}
Sys.setenv(SPOTIFY_CLIENT_ID = '72409a2540ff40549726df49c2d7f4ca')
Sys.setenv(SPOTIFY_CLIENT_SECRET = '10edfe439e5a4ec5ac3e74b49a5aaf9f')

access_token <- get_spotify_access_token()
```

```{r}
# testing
kendrick <- get_artist_audio_features('kendrick lamar')

summary(kendrick)
head(kendrick)

kendrick %>%
  count(album_release_year, sort = TRUE) %>%
  
  ggplot(mapping = aes(x = album_release_year, y = n))
```

```{r}
# finding playlist info
```

